Efficient Community Formation \\ for Web Services

### 2013-12-21 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

\textbf{Contributions.} In this paper, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating from the community. In other words, the coalition is
made efficient if all the members are satisfied. We analyze the
game model using two scenarios. The first one simply considers one
community and many web services interested to join it. The second
scenario, which generalizes the first one, includes the
possibility of joining different already established communities.
We first propose a representation function for communities of web
services based on their QoS attributes. By using this function, we
can evaluate the $worth$ of each community of web services. When
facing new membership requests, a typical community master checks
whether the new coalition having the old and new set of web
services will keep the community stable or not. The community
coordinate will reject the membership requests if it finds out that
the new coalition would be unstable, preventing $any$ subset of
web services from gaining significantly more by deviating from the
community and joining other communities or forming new ones. The
computation of solutions for cooperative game theory problems is
combinatorial in nature and proven to be NP-complete
\cite{Algorithmic}, making this computation impractical in real
world applications. However, using the concepts of coalition
stability, we propose approximation algorithms running in
polynomial time providing web services and community coordinators with
applicable and near-optimal decision making mechanisms.

@@

Our algorithm works as follows. Given an  established community
with a master and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity of our game having characteristic function
where the new member is added. In the equation, let $C$  be our
community members before having the new web service join the
community. Let  ${i}$ be the new web service, and then verify the
equation for $S$, setting $ S = T / W1 $ where $W1$ is the set of
all possible subsets of the set $N$ having the size $1$. We can
relax the equation a bit by adding a constant $\epsilon$ to the
left side of the equation. We call this method \emph{Depth-1
Convex-Checker} algorithm. If the equation is satisfied for all
$W1$, we let the new web service join our community, since the web
service will contribute positively enough to make our new
community stable. Since only subsets of size $1$ are checked, the
following Proposition holds.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms in \cite{Sandholm1999209,
DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

In coalition-formation games, formation of the coalitions is the
most important aspect. The solutions focus on maximizing the
social welfare. For any coalition structure $\pi$, let
$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
which represents the \emph{social welfare}. The solution concepts
in this area deal with finding the maximum value for the social
welfare over all the possible coalition structures $\pi$. There
are $centralized$ algorithms for this end, but these approaches
are generally NP-complete. The reason is that the number of all
possible partitions of the set $N$ grows exponentially with the
number of players in $N$, and the centralized algorithms need to
iterate through all these partitions.
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
In our model, we propose using a distributed algorithm where each
community master and web service can be a decision maker and
decide for its own good. The aim is to find less complex and
distributed algorithms for forming web services
coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
The distributed merge-and-split algorithm in
\cite{DBLP:journals/igtr/AptW09} suits our application very well.
It keeps splitting and merging coalitions to partitions which are
preferred by all the players inside those coalitions.

@@

The valuation function $v(C)$ for this scenario is the same as
\emph{``Web Services and One Community''} scenario. However, in
order to prevent master web services joining the same community,
we set $v(C) = 0$ when $C$ has either none, or more than one
master web service as member.

@@

One way for communities to ensure  stability could be  by applying
a tax, $\epsilon$ amount of cost for web services changing
communities which would make deviation a costly act. However this
would require all community coordinators to agree on a same amount
of taxation, being governed by some external entities or web
services would join communities with lesser amount of tax. Another
viable solution to our scenario is to stabilize the game using
external subsidies. The reason a game is not stable is that the
community is not making enough revenue to allocate  enough gain to
the players. A community master can subside its community with a
constant coefficient value of $\lambda$.

@@

Obviously with a big number of $\lambda$, it is always possible to
stabilize the community. However, this can be a costly act for
community masters so they are interested in the minimum subside
value of $\lambda$ making the game stable. Subsiding or taxing in
order to reduce the bargaining power of sub coalitions are called
$taxation$ \cite{eps346856} methods.

>>>>

\textbf{Contributions.} In this paper, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating from the community. In other words, the coalition is
made efficient if all the members are satisfied. We analyze the
game model using two scenarios. The first one simply considers one
community and many web services interested to join it. The second
scenario, which generalizes the first one, includes the
possibility of joining different already established communities.
We first propose a representation function for communities of web
services based on their QoS attributes. By using this function, we
can evaluate the $worth$ of each community of web services. When
facing new membership requests, a typical community coordinator checks
whether the new coalition having the old and new set of web
services will keep the community stable or not. The community
coordinate will reject the membership requests if it finds out that
the new coalition would be unstable, preventing $any$ subset of
web services from gaining significantly more by deviating from the
community and joining other communities or forming new ones. The
computation of solutions for cooperative game theory problems is
combinatorial in nature and proven to be NP-complete
\cite{Algorithmic}, making this computation impractical in real
world applications. However, using the concepts of coalition
stability, we propose approximation algorithms running in
polynomial time providing web services and community coordinators with
applicable and near-optimal decision making mechanisms.

@@

Our algorithm works as follows. Given an established community
with a coordinator and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity of our game having characteristic function
where the new member is added. In the equation, let $C$  be our
community members before having the new web service join the
community. Let  ${i}$ be the new web service, and then verify the
equation for $S$, setting $ S = T / W1 $ where $W1$ is the set of
all possible subsets of the set $N$ having the size $1$. We can
relax the equation a bit by adding a constant $\epsilon$ to the
left side of the equation. We call this method \emph{Depth-1
Convex-Checker} algorithm. If the equation is satisfied for all
$W1$, we let the new web service join our community, since the web
service will contribute positively enough to make our new
community stable. Since only subsets of size $1$ are checked, the
following Proposition holds.

@@

In this scenario, we consider multiple communities managed by
multiple coordinators, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, community coordinators form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms in \cite{Sandholm1999209,
DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

In coalition-formation games, formation of the coalitions is the
most important aspect. The solutions focus on maximizing the
social welfare. For any coalition structure $\pi$, let
$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
which represents the \emph{social welfare}. The solution concepts
in this area deal with finding the maximum value for the social
welfare over all the possible coalition structures $\pi$. There
are $centralized$ algorithms for this end, but these approaches
are generally NP-complete. The reason is that the number of all
possible partitions of the set $N$ grows exponentially with the
number of players in $N$, and the centralized algorithms need to
iterate through all these partitions.
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
In our model, we propose using a distributed algorithm where each
community coordinator and web service can be a decision maker and
decide for its own good. The aim is to find less complex and
distributed algorithms for forming web services
coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
The distributed merge-and-split algorithm in
\cite{DBLP:journals/igtr/AptW09} suits our application very well.
It keeps splitting and merging coalitions to partitions which are
preferred by all the players inside those coalitions.

@@

The valuation function $v(C)$ for this scenario is the same as
\emph{``Web Services and One Community''} scenario. 
%However, in order to prevent master web services joining the same community, we set $v(C) = 0$ when $C$ has either none, or more than one master web service as member.

@@

One way for communities to ensure  stability could be  by applying
a tax, $\epsilon$ amount of cost for web services changing
communities which would make deviation a costly act. However this
would require all community coordinators to agree on a same amount
of taxation, being governed by some external entities or web
services would join communities with lesser amount of tax. Another
viable solution to our scenario is to stabilize the game using
external subsidies. The reason a game is not stable is that the
community is not making enough revenue to allocate  enough gain to
the players. A community coordinator can subside its community with a
constant coefficient value of $\lambda$.

@@

Obviously with a big number of $\lambda$, it is always possible to
stabilize the community. However, this can be a costly act for
community coordinators so they are interested in the minimum subside
value of $\lambda$ making the game stable. Subsiding or taxing in
order to reduce the bargaining power of sub coalitions are called
$taxation$ \cite{eps346856} methods.
